MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-25 paper.Rmd
Better footnote.

We created a suite of `R` packages 
(some of which are generally useful and available through 
[CRAN][link-cran],
others of which are focused on SEA and available on GitHub)
to assist SEA practitioners as they analyze 
energy movement through society. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the packages enable, for the first time, scalable SEA.
We used the new packages to create the "PFU Database,"^[Technically speaking, 
we create data frames of matrices, 
not an SQL or similar database.] 
a new resource for the SEA community [@Marshall:2023aa].

>>>>

We created a suite of `R` packages 
(some of which are generally useful and available through 
[CRAN][link-cran],
others of which are focused on SEA and available on GitHub)
to assist SEA practitioners as they analyze 
energy movement through society. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the packages enable, for the first time, scalable SEA.
We used the new packages to create the "PFU Database,"^[Technically speaking, 
we create [matsindf][link-matsindf]-style data frames, 
not an SQL or similar database.] 
a new resource for the SEA community [@Marshall:2023aa].
